---
title: 'Homework 2'
author: "Narayan Gopinathan"
date: "September 20, 2019"
output: 
  html_document:

---

```{r, warning = FALSE, echo = FALSE}
library(gapminder)
library(tidyverse)

```

# Exercise 1

## 1.1

```{r}
gapminder %>%
  filter(year >= 1970) %>%
  filter(year < 1980) %>%
  filter(country =='United States'|country=='Canada'|country=='Mexico')
```

## 1.2

```{r}

```

## 1.3

```{r}

```

## 1.4

```{r}

```

## 1.5

```{r}

```

# Exercise 2

```{r}

```

# Exercise 3

```{r fig.width = 5, fig.height = 2}
gapminder  %>%
  select(lifeExp, year) %>%
    ggplot(aes(year, lifeExp))+
    geom_point(alpha = 0.1)
        scale_x_log10("GDP per capita", labels = scales::dollar_format())
```

Homework 2 Code
---
title: 'Homework 2'
author: "Narayan Gopinathan"
date: "September 20, 2019"
output: 
  html_document:

---

```{r, warning = FALSE, echo = FALSE}
library(gapminder)
library(tidyverse)

```

# Exercise 1

## 1.1

```{r}
gapminder %>%
  filter(year >= 1970) %>%
  filter(year < 1980) %>%
  filter(country =='United States'|country=='Canada'|country=='Mexico')
```

## 1.2

```{r}
gapminder %>%
  filter(year >= 1970) %>%
  filter(year < 1980) %>%
  filter(country =='United States'|country=='Canada'|country=='Mexico') %>%
  select(country, gdpPercap)


ggplot(gapminder, aes(gdpPercap, lifeExp)) +
  geom_point(alpha = 0.1) +
  scale_x_log10("GDP per capita", labels = scales::dollar_format())

## 1.5

```{r fig.width = 5, fig.height = 2}
gapminder %>%
  filter(country == 'Canada') %>%
  select(lifeExp, gdpPercap) %>%
    ggplot(aes(gdpPercap, lifeExp))+
      geom_point(alpha = 0.1) + 
      scale_x_log10("GDP per capita", labels = scales::dollar_format())
```
      
# Exercise 2

```{r}

```

# Exercise 3

```{r fig.width = 5, fig.height = 2}
gapminder  %>%
  select(lifeExp, year) %>%
    ggplot(aes(year, lifeExp))+
    geom_point(alpha = 0.1)
        scale_x_log10("GDP per capita", labels = scales::dollar_format())
```



