---
title: "A1E3v2 IOSlides"
author: "Narayan"
date: "9/15/2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.


## 



### Slide with bullet points
- I am Narayan.
- This is my first slide in RStudio IOSlides.

## 

### Graph of Gapminder data

```{r, echo = FALSE, message =FALSE, warning = FALSE}
library(gapminder)
library(ggplot2)
data(gapminder)
ggplot(gapminder,aes(x = year, y=lifeExp))+
  geom_point()
```



## Slide with R Output

```{r gapminder, echo = TRUE}
summary(gapminder)
```



## Slide with Plot

```{r pressure}
plot(pressure)